Thermodynamic response functions in a cell fluid model

### 2024-09-13 paper_text.tex
adjust references according to ujp guide

>>>>

\begin{thebibliography}{9}
	\bibitem{KozitskyKozlovskiiDobush2018book} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
	\href{https://link.springer.com/chapter/10.1007/978-3-319-61109-9_11}{Phase transitions in a continuum curie-weiss system: A quantitative analysis.}, in: L.~A.~Bulavin, A.~V.~Chalyi (Eds.), \textit{Modern Problems of Molecular Physics} (Springer, 2018) [doi: 10.1007/978-3-319-61109-9\_11]

	\bibitem{KozitskyKozlovskiiDobush2020} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
	\href{https://icmp.lviv.ua/journal/zbirnyk.102/23502/abstract.html}{A phase transition in a Curie-Weiss system with binary interactions.}, \textit{Condens.
	Matter Phys.} \textbf{23}, 23502 (2020) [doi: 10.5488/CMP.23.23502]

	\bibitem{KozlovskiiDobush2020} M.~Kozlovskii, O.~Dobush.
	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase
	behavior of a cell fluid model with modified Morse potential.}, \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]

	\bibitem{PylyukDobush2020} I.~Pylyuk, O.~Dobush. \href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.}, \textit{Ukr. J. Phys.} \textbf{65}, 1080 (2020) [doi: 10.15407/ujpe65.12.1080]

	\bibitem{PylyukEtAlJML2023}	I.~Pylyuk, M.~Kozlovskii, O.~Dobush, M.~Dufanets.
	\href{https://www.sciencedirect.com/science/article/pii/S0167732223011261}{Morse fluids in the immediate vicinity of the critical point: Calculation of thermodynamic coefficients.}, \textit{J. Mol. Liq.} \textbf{385}, 122322 (2023) [doi: 10.1016/j.molliq.2023.122322]

	\bibitem{PylyukKozlovskiiDobushUJP2023b} I.~Pylyuk, M.~Kozlovskii, O.~Dobush.
	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2023197}{Analytic calculation of the critical temperature and estimation of the critical region size for a fluid model.}, \textit{Ukr. J. Phys.} \textbf{68}, 601 (2023) [doi: 10.15407/ujpe68.9.601]

	\bibitem{StrokerMeier2021} P.~Str\"oker, K.~Meier.
	\href{https://link.aps.org/doi/10.1103/PhysRevE.104.014117}{Classical
	statistical mechanics in the grand canonical ensemble.}, \textit{Phys. Rev. E} \textbf{104}, 014117 (2021) [doi: 10.1103/PhysRevE.104.014117]

	\bibitem{Morse1929}	P.~M.~Morse. \href{https://link.aps.org/doi/10.1103/PhysRev.34.57}{Diatomic
	molecules according to the wave mechanics. II. Vibrational levels.}, \textit{Phys.
	Rev.} \textbf{34}, 57 (1929) [doi: 10.1103/PhysRev.34.57]

	\bibitem{MartinezValenciaEtAl2013} A.~Martínez-Valencia, M.~González-Melchor, P.~Orea, J.~López-Lemus.
	\href{https://doi.org/10.1080/08927022.2012.702422}{Liquid–vapour interface
	varying the softness and range of the interaction potential.}, \textit{Molecular
	Simulation} \textbf{39}, 64 (2013) [doi: 10.1080/08927022.2012.702422]

	\bibitem{BiswasHamann1985} R.~Biswas, D.~R. Hamann.
	\href{https://link.aps.org/doi/10.1103/PhysRevLett.55.2001}{Interatomic
	potentials for silicon structural energies.}, \textit{Phys. Rev. Lett.} \textbf{55}, 2001 (1985) [doi: 10.1103/PhysRevLett.55.2001]

	\bibitem{Lim2005} T.-C. Lim. \href{https://acta-arhiv.chem-soc.si/52/52-2-149.htm}{Approximate
	relationships between the generalized Morse and the extended-Rydberg potential energy functions.}, \textit{Acta Chim. Slov.} \textbf{52}, 149 (2005)

	\bibitem{KozlovskiiDobush2016} M.~Kozlovskii, O.~Dobush.
	\href{https://www.sciencedirect.com/science/article/pii/S0167732215312101}{Representation of the grand partition function of the cell model: The state equation in the mean-field approximation}, \textit{J. Mol. Liq.} \textbf{215}, 58 (2016) [doi: j.molliq.2015.12.018]

	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter} (Academic Press, 2013) [ISBN: 9780123870339]

	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids}, \textit{J. Chem. Phys.} \textbf{138}, 194502 (2013) [doi: 10.1063/1.4803855]

\end{thebibliography}
